Preventing a Nuclear ISIL: \\Recommendations for United States Policy

### 2015-05-11 draft.tex
Added in Appendix H - Table of Bilateral Military Relations.

\chapter[Appendix H: ????????]{?????????} \label{app:relations_table}

\section{???????????  Missing ??????????}

???????????  Missing ??????????

>>>>

\chapter[Appendix H: Bilateral Relations between the U.S. \& Strategic Countries]{Bilateral Relations between the U.S. \&  Strategic Countries} \label{app:relations_table}

As a concise summary of U.S. foreign relations (as they relate to ISIL acquisition of nuclear weapons), a matrix of Bilateral Relations between the U.S. and Strategic Countries is provided in \autoref{tab:bilateral_table}.
\begin{table}[h]
\resizebox{1.38\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|}
\multicolumn{1}{|c|}{Country}                               & \multicolumn{1}{c|}{Relationship with US}                                                                                                                                                                                                                                                                                                                                                                                               & \multicolumn{1}{c|}{Military and Nuclear Capabilities}                                                                                                                                                                                                                                                                                                        & \multicolumn{1}{c|}{ISIL Position}                                                                                                                                                                                                                                                                                                                                                                      \\ \hline
Russia                                                      & \begin{tabular}[c]{@{}l@{}}Strained relationship due to economic sanctions, imposed for Russia’s annexation of Crimea.\\ Predicted power struggle for new world order, and a historical rival.\\ Agreed to maintain dialogue in areas of terrorism, energy security, and\\ 			nuclear non-proliferation issues (Iran, North Korea).\end{tabular}                                                                                        & \begin{tabular}[c]{@{}l@{}}Military capability rank: 2 \cite{U.S.CentralIntelligenceAgency2012} (after the U.S.)\\ Defense spending: US\$84.5 billion (2014) \cite{StockholmInternationalPeaceResearchInstitute2014}\\ Total NW inventory: 7,500; deployed strategic: 1,780 \cite{FederationofAmericanScientists2015}\end{tabular}                                                                                                                                               & \begin{tabular}[c]{@{}l@{}}More than 500 Russians are believed to have joined ISIL.\\ Russia considering supplying military equipment to Libya and Iraq. Agreed\\ 			to work together with  US on facing ISIL.\end{tabular}                                                                                                                                                                             \\ \hline
China                                                       & \begin{tabular}[c]{@{}l@{}}China and the US have a close economic partnership. \\ Two-way trade between China and the United States is \\ over US\$590 billion in 2014. China is the second largest export country (after Canada).\end{tabular}                                                                                                                                                                                         & \begin{tabular}[c]{@{}l@{}}Military capability rank: 3 \cite{U.S.CentralIntelligenceAgency2012}\\ Defense Spending: US\$145 billion (2014)\\ China has been increasing its annual military budget \\ over the last two decades. Total NW inventory: 250; deployed strategic: 0 \cite{StockholmInternationalPeaceResearchInstitute2014}\end{tabular}                                                                                            & \begin{tabular}[c]{@{}l@{}}Chinese Muslim Uyghur militants trying to flee the country and join ISIL\\ 			training camps in preparation for attacks back home.\end{tabular}                                                                                                                                                                                                                              \\ \hline
\begin{tabular}[c]{@{}l@{}}United\\ 			Kingdom\end{tabular} & \begin{tabular}[c]{@{}l@{}}Special relationship; close allies encompassing various issues, \\ including political and military, dating back to Churchillian era.\end{tabular}                                                                                                                                                                                                                                                           & \begin{tabular}[c]{@{}l@{}}Military capability rank: 5 \cite{U.S.CentralIntelligenceAgency2012} \\ Defense Spending: US\$51.5 billion (2014) Talks of spending reduction.\\ Total NW inventory: 225; deployed strategic: 160 \cite{FederationofAmericanScientists2015}\end{tabular}                                                                                                                                              & \begin{tabular}[c]{@{}l@{}}The U.K. government declared ISIL a terrorist organization.\\ Hundreds of U.K. citizens are estimated to have joined ISIL.\\ 			U.K. citizens have been killed or kidnapped by ISIL.\end{tabular}                                                                                                                                                                            \\ \hline
France                                                      & \begin{tabular}[c]{@{}l@{}}France is the U.S.’ oldest ally, relationship remains active and friendly. \\ 			France supported U.S. on various issues, but France was skeptical of U.S. invasion of Iraq.\end{tabular}                                                                                                                                                                                                                    & \begin{tabular}[c]{@{}l@{}}Military capability rank: 6 \cite{U.S.CentralIntelligenceAgency2012} \\ 			Defense spending: US\$40 billion (2014)\\ 			Total NW inventory: 300; deployed strategic: 290 \cite{StockholmInternationalPeaceResearchInstitute2014}\end{tabular}                                                                                                                                                                       & \begin{tabular}[c]{@{}l@{}}France supported US-led coalition against ISIL.\\ 			France’s colonial history in Africa made it pivotal in the fight against\\ 			ISIL and Islamic terrorism in Africa. ISIL called for French\\ 			Muslim to join the group and perform terror attacks within France.\end{tabular}                                                                                         \\ \hline
\begin{tabular}[c]{@{}l@{}}North\\ 			Korea\end{tabular}    & \begin{tabular}[c]{@{}l@{}}North Korea has repeatedly threatened the U.S. with nuclear attacks.	\\  Relationship between the two countries are negative.		North Korea is not a party to NPT.\end{tabular}                                                                                                                                                                                                                               & \begin{tabular}[c]{@{}l@{}}Military capability rank: 36 \cite{U.S.CentralIntelligenceAgency2012} \\ 			Defense Spending: US\$5.5 billion (2014) \cite{U.S.CentralIntelligenceAgency2012} \\ Total NW inventory: 6-8; deployed strategic: 0 \cite{StockholmInternationalPeaceResearchInstitute2014} \\ 			Recent reports suggest that North Korea may have up \\ to 20 nuclear warheads and could built as many as 100 by 2020 \cite{TheEditorialBoard2015a}.\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}North Korea has publicly condemned US effort in annihilating ISIL.\\ 			However, no concrete information has been gathered whether North\\ 			Korea and ISIL have made significant contact. U.S. worries North\\ 			Korea will sell nuclear technology to non-state actors.\end{tabular}                                                                                     \\ \hline
Israel                                                      & U.S. was the first country that that recognized independence of Israel in 1948.                                                                                                                                                                                                                                                                                                                                                         & \begin{tabular}[c]{@{}l@{}}Military capability rank: 11 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$17 billion (2014)\\ 			Total NW inventory: 80; deployed strategic: 0 \cite{StockholmInternationalPeaceResearchInstitute2014}.\end{tabular}                                                                                                                                                                          & \begin{tabular}[c]{@{}l@{}}Report from the UN reveals that the Israeli Defense Forces\\ (IDF) maintained regular contact with members of ISIL since May 2013.\end{tabular}                                                                                                                                                                                                                              \\ \hline
India                                                       & \begin{tabular}[c]{@{}l@{}}‘Global strategic partnership’ based on shared democratic values and\\ 			increasing convergence of interests on bilateral, regional and global issues. \\ Historically, India was close ally with Russia then\\ 			pioneered the Non-Aligned Movement (NAM).\end{tabular}                                                                                                                                   & \begin{tabular}[c]{@{}l@{}}Military capability rank: 4 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$38 billion (2014)\\ 			Total inventory: 90 - 100; deployed strategic: 0 \cite{StockholmInternationalPeaceResearchInstitute2014}.\end{tabular}                                                                                                                                                                       & \begin{tabular}[c]{@{}l@{}}ISIL identified Central Asia, including area north of India, as ‘a ripe recruitment area’. \\ 			The government considered ISIL as a periphery issue, but\\ 			ISIL’s plan of expansion might include areas in India.\end{tabular}                                                                                                                                           \\ \hline
Pakistan                                                    & \begin{tabular}[c]{@{}l@{}}Over the decades, Pakistan has been a great ally to the U.S., but there\\ 			are instances where the two countries disagreed. U.S. views Pakistan \\ as its ally, but worries about the threat of terrorism in\\ 			Pakistan. Pakistan has received US\$28.4 billion in military and non-military aid post 9/11.\end{tabular}                                                                                & \begin{tabular}[c]{@{}l@{}}Military capability rank: 17 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$7 billion (2014)\\ 			Pakistan is not a party to NPT.\\ 			Total NW inventory: Unknown.\end{tabular}                                                                                                                                                                & \begin{tabular}[c]{@{}l@{}}Many members of Pakistan’s terrorist groups have joined ISIL. ISIL’s leaked \\ secret memo spelled out the master plan on how to wage war\\ 			against the Pakistani military while trying to join forces with\\ 			local militants.\end{tabular}                                                                                                                            \\ \hline
Iran                                                        & \begin{tabular}[c]{@{}l@{}}Long and unpleasant history; current concerns about Iran are its\\ 			support for terrorism, pursuit of nuclear weapons, it’s opposition \\ towards Israelis and Arabs, and the country’s poor human rights record.\end{tabular}                                                                                                                                                                             & \begin{tabular}[c]{@{}l@{}}Military capability rank: 23 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$6.3 billion (2014)\\ 			Currently, Iran and P5+1 countries are negotiating a nuclear deal to halt\\ 			Iran’s nuclear development.\end{tabular}                                                                                                                    & \begin{tabular}[c]{@{}l@{}}Iran and ISIL are fighting for the crown of militant Islam. In this\\ 			case, enemy’s enemy is not our friend. The goal for the US is to\\ 			defeat ISIL and to halt Iran’s nuclear program.\end{tabular}                                                                                                                                                                  \\ \hline
Iraq                                                        & \begin{tabular}[c]{@{}l@{}}The Strategic Framework Agreement for a Relationship of Friendship and\\ 			Cooperation between the US and the Republic of Iraq guides the\\ 			overall political, economic, cultural, and security ties with\\ 			Iraq.  This agreement is designed to help the Iraqi people stand\\ 			on their own and reinforce Iraqi sovereignty, while protecting 			U.S. interests in the Middle East.\end{tabular} & \begin{tabular}[c]{@{}l@{}}Military capability rank: 112 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$6 billion (2014)\\ 			The US has been heavily investing in reforming and assisting the\\ 			country’s military capabilities.\end{tabular}                                                                                                                          & \begin{tabular}[c]{@{}l@{}}ISIL is carving its territory from Iraq. The weak governance of Iraq\\ 			instigated ISIL’s ambition. has been battling ISIL aided by a\\ 			coalition made up of Shiite militiamen and volunteers.\end{tabular}                                                                                                                                                             \\ \hline
Syria                                                       & \begin{tabular}[c]{@{}l@{}}The U.S.-Syria relationship is negative after having suspended diplomatic relations in 2014. \\ 			The U.S. has imposed economic sanction to Syria since 2004 due to\\ 			Syria’s involvement in harboring terrorist groups. The U.S. is\\ 			deeply opposed to President Bashar al-Assad’s regime,\\ 			specifically regarding chemical weapons use.\end{tabular}                                     & \begin{tabular}[c]{@{}l@{}}Military capability rank: 42 \cite{U.S.CentralIntelligenceAgency2012}\\ 			Defense spending: US\$1.9 billion (2014)\\ Syrian’s military hardware are mostly acquired from Russia and Iran.\\ 			Despite losing its military personnel, the Syrian military has been said\\ 			to become more flexible and capable especially in anti-guerilla warfare.\end{tabular} & \begin{tabular}[c]{@{}l@{}}ISIL is gaining foothold in Syria, and carving its territory from the\\ 			country. Hence, Syrian government is fighting ISIL. The U.S. has\\ 			floated the idea to train the Syrian military opposition, and even\\ 			the Syrian military itself, in order to fight ISIL. Syria views\\ 			U.S.-led coalition against ISIL as a threat to their sovereignty.\end{tabular} \\ \hline
\caption{Matrix of Bilateral Relations between the U.S. and Strategic Countries}
\label{tab:bilateral_table}
